% !TEX program = xelatex


\documentclass{resume}
\newcommand\quelle[1]{{%
		\unskip\nobreak\hfil\penalty50
		\hskip2em\hbox{}\nobreak\hfil #1%
\parfillskip=0pt \finalhyphendemerits=0 \par}}

%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Junhao Lin(Eric Lin)}

\basicInfo{
	\email{ericlin1001@qq.com} \textperiodcentered\ 
	\phone{(+86) 135-8053-2764} 
	%\textperiodcentered\ 
	%\linkedin[billryan8]{https://www.linkedin.com/in/billryan8}}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{SUN YAT-SEN University (SYSU)}, Guangzhou, China}{2015 -- Present}
\textit{Master student} in School of Data and Computer Science (SDCS), expected July 2018
\datedsubsection{\textbf{SUN YAT-SEN University (SYSU)}, Guangzhou, China}{2011 -- 2015}
\textit{B.S.} in School of Information Science and Technology (SIST)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Adaptive Parallel Differential Evolution for PEC}}{Mar. 2015 -- Jul. 2016}
% TODO:: Is Maintainer the exact role.
\role{C++, MPI, Maintainer}{Individual Academic Project}
A parallel program running in cluster to solve Power Electronic Circuit(PEC) problem, \url{https://github.com/ericlin1001/AdaptivePDE}
\begin{itemize}
	\item Parallelized Differential Evolution(DE) algorithm, the speedup was nearly half of the number of CPU cores
	\item Support for adaptively distributing tasks among cores, efficiently utilizing all CPU cores
	\item Defined an unified Json format for setting up all DE's arguments
	\item Published corresponding paper: \textit{Parallel Differential Evolution Based on Distributed Cloud Computing Resources for Power Electronic Circuit Optimization} in GECCO '16 Companion 
\end{itemize}

%\datedsubsection{\textbf{Remote Control}}{Mar. 2016 -- Apr. 2016}
% TODO:: Is Maintainer the exact role.
%\role{Python, Maintainer}{Individual Project}
%A remote control software, \url{https://github.com/ericlin1001/RemoteControl}
%\begin{itemize}
%	\item Implemented real-time screen capturing
%	\item Support for mouse and keyboard synchronizing
%	\item Support for highlighting mouse click position
%\end{itemize}

\datedsubsection{\textbf{Help-Each-Other}}{Jul. 2013 -- Dec. 2013}
\role{Php, Project Manager}{Team Project, collaborated with three classmates}
A web application providing a way to facilitate people help each other, \url{https://github.com/ericlin1001/HelpEachOtherProject}
\begin{itemize}
	\item Implemented task management system, allowed users to pose and accept tasks
\item Support user ranking based on the number of tasks the user finished
\item Implemented online chat system, feedback system
%\item Support for feedback.
\end{itemize}
\datedsubsection{\textbf{Eric-OS}}{Jan. 2013 -- Jun. 2013}
\role{Asm, C, Maintainer}{Term Project, Individual Project}
A basic Operating System(OS), \url{https://github.com/ericlin1001/EricOSProject}
\begin{itemize}
		% write a readme for the project.
	\item Implemented Buddy based Memory Management, support dynamic memory allocating
	\item Support reading files in FAT12 Filesystem 
	\item Implemented Process Scheduling, Inter-process Communication, and standard input output(IO)
	\item Used as an standard example by the teacher, and I was invited to explain it to the whole class
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
% \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
	\item Technologies: C++/C, Python, Php, MySQL, Asm, Java, HTML, Matlab, Shell Scripting, Git, Json, XML, Clisp, Autoit, LAMP server administration
\end{itemize}

\section{\faHeartO\ Honors and Awards}

%\datedline{Published \textit{Parallel Differential Evolution Based on Distributed Cloud Computing Resources for Power Electronic Circuit Optimization} in GECCO '16 Companion}{Jul. 2016}
%\par Published \textit{Parallel Differential Evolution Based on Distributed Cloud Computing Resources for Power Electronic Circuit Optimization} in GECCO '16 Companion \hfill Jul. 2016 \par
%#OK: \textit{Publish Parallel Differential Evolution Based on Distributed Cloud Computing Resources for Power Electronic Circuit Optimization} in GECCO '16 Companion \hfill {Jul. 2016}
\par
\datedline{2015-2016 SUN YAT-SEN University Outstanding Graduate Scholarship, top 10\%}{Jun. 2016}
	\datedline{2011-2012 SUN YAT-SEN The Second Prize Scholarship, top 15\%}{Jun. 2012}


		\section{\faInfo\ Miscellaneous}
		\begin{itemize}[parsep=0.5ex]
			%\item Blog: \url{https://ericlin1001.github.io}
			\item GitHub: \url{https://github.com/ericlin1001}
			\item Languages: English - Fluent, Mandarin - Native speaker
		\end{itemize}

		%% Reference
		%\newpage
		%\bibliographystyle{IEEETran}
		%\bibliography{mycite}
		\end{document}
